---
title: "Stomach and lung cancer incidence/mortality clustering results"
author: "Insang Song"
date: 11-07-2022
theme: "spacelab"
format: 
  html:
    toc: true
    embed-resources: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

- General description
    - This document includes all the LISA (aka Local Moran's _I_) maps in South Korea at district level.
    - Ongjin, Ulleung, Jeju, and Seogwipo were excluded.
    - We used the age-standardized mortality/incidence rates in the data
        - For the district unification, we calculated population-weight-averaged rates in any districts that were subject to the calculation.

- Change log
    - 07/14/2022
        - Updated data
    - 10/26/2022
        - Double sensitivity: variable order, education-only in M1
        - Added labels of the number of districts 
    - 11/07/2022
        - Directly converted SaTScan outputs into sggid lists then referring to it for plotting


```{r}
source('../Base/base_functions.R')
options(repos = 'https://cran.seoul.go.kr')
if (!require(pacman)) { install.packages('pacman') } 

p_load(tidyverse, sf, stars, raster, starsExtra, readxl, here, tmap, stargazer, smerc, DClusterm, kableExtra, patchwork, rmapshaper, spdep)

dirpattern = "/mnt/c/Users/%s/"
username = 'sigma'
basedir = sprintf(dirpattern, username)
rdatafiles = list.files(path = str_c(basedir, 'Documents/GP/'), pattern = '*.RData', full.names = TRUE)
geopath = str_c(basedir, "OneDrive/Data/Korea/")
drive = str_c(basedir, "OneDrive/NCC_Project/CancerClustering/")
geopath = str_c(basedir, "OneDrive/Data/Korea/")
dbdir = drive  
rdsdir = drive #sprintf("/mnt/c/Users/%s/OneDrive/NCC_Project/CancerClustering/", username)

```


```{r}
load(str_c(drive, '/Manuscript/Clustering_Base_sf_091522.RData'))

covar_origin_10_fc = covar_origin_10_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.1, keep_shapes = TRUE)
covar_origin_05_fc = covar_origin_05_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.1, keep_shapes = TRUE)
covar_origin_00_fc = covar_origin_00_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.1, keep_shapes = TRUE)

clear_input = function(filepath, alpha = 0.01, locmin = 2) {
    # alpha: significance level
    # locmin: how many points should be included at least?
    res = read_rds(filepath)
    labels = as.data.frame(str_split_fixed(res$analysis_title, "_", 6))
    colnames(labels) = c("cancertype", "period", "measure", "target", "sex", "vset")
    res = res %>%
          bind_cols(labels, .) %>%
          filter(pvalue <= alpha & number_locs >= locmin)
    resl = res %>% split(., .$analysis_title)
    return(resl)
}

p_v0_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_uncontrolled_resid.rds"))
p_va_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_age_resid.rds"))
p_ve_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_educ_resid.rds"))
p_venv_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_environ_resid.rds"))
p_vb_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_behavior_resid.rds"))
p_v1_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset1_resid.rds"))
p_v2_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset2_resid.rds"))
p_v3_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset3_resid.rds"))
p_v4_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset4_resid.rds"))
p_v5_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_stomach_diagnosis_resid.rds"))


```

# Overview
- Incidence and mortality rates: (Sum of cases) / (Sum of the population)
- All inclusive variables
    - Set 1: elderly population rate (%) and higher than bachelor's degree (%)
    - Set 2: Set 1 + including emission, residential exposure, and NDVI
    - Set 3: for periods 2 and 3. All but insurance premium and stomach cancer screening
    - Set 4: for period 3 only. All variables.

## Cleaning functions
```{r Lung cancer cluster plots (incidence), fig.width=12, fig.height = 5.6}

# Extract LISA sf objects
extr_lisa_sf = function(fc00, fc05, fc10, flag = "ragest_i_") {
    cl00 = fc00 %>% colnames %>% .[grep(flag, .)]
    cl05 = fc05 %>% colnames %>% .[grep(flag, .)]
    cl10 = fc10 %>% colnames %>% .[grep(flag, .)]
    cn_common = intersect(colnames(fc00), colnames(fc05))

    fc00 = fc00 %>% dplyr::select(all_of(cn_common), all_of(cl00))
    fc05 = fc05 %>% dplyr::select(all_of(cn_common), all_of(cl05))
    fc10 = fc10 %>% dplyr::select(all_of(cn_common), all_of(cl10))
    
    fc00tt = 
        cl00 %>% split(.,.) %>%
            lapply(function(x) { map_lisa(fc00, x, return_sf = TRUE) }) %>%
            do.call(rbind, .) %>%
            mutate(period = 1,
                   year = "1999-2003") %>%
            dplyr::select(-all_of(cl00))
    fc05tt = 
        cl05 %>% split(.,.) %>%
            lapply(function(x) { map_lisa(fc05, x, return_sf = TRUE) }) %>%
            do.call(rbind, .) %>%
            mutate(period = 2,
                   year = "2004-2008") %>%
            dplyr::select(-all_of(cl05))
    fc10tt = 
        cl10 %>% split(.,.) %>%
            lapply(function(x) { map_lisa(fc10, x, return_sf = TRUE) }) %>%
            do.call(rbind, .) %>%
            mutate(period = 3,
                   year = "2009-2013") %>%
            dplyr::select(-all_of(cl10))

    st_crs(fc00tt) = st_crs(fc05tt) = st_crs(fc10tt)
    fc0010tt = rbind(fc00tt, fc05tt) %>% rbind(fc10tt) %>%
        mutate(cancer = as.vector(str_extract_all(analysis_title, "(Lung|Stomach)", simplify = T)),
               datatype = ifelse(grepl('_i_', analysis_title), 'incidence', 'mortality'),
               valuetype = ifelse(grepl("^n_", analysis_title), "Count", "Rate")
               )
    return(fc0010tt)    
}

# Extract SSS sf objects
extr_sss_sf = function(fc, resl, flag = "_i_") {
    names_extr = names(resl) %>% grep(flag, .)

    fctt = 
        resl[names_extr] %>%
        #lapply(function(x) x[[1]]) %>%
        #Filter(Negate(is.null), .) %>%
        lapply(function(x) df_satscan_primary(fc, x, area = TRUE) )   
    fctt = fctt %>%
        do.call(rbind, .) %>%
        mutate(cancer = as.vector(str_extract_all(analysis_title, "(Lung|Stomach)", simplify=T)),
               datatype = ifelse(grepl('_i_', analysis_title), 'incidence', 'mortality'),
               period = case_when(
                            grepl("_p1_", analysis_title) ~ 1,
                            grepl("_p2_", analysis_title) ~ 2,
                            grepl("_p3_", analysis_title) ~ 3,
                            TRUE ~ 999),
               year = case_when(
                            grepl("_p1_", analysis_title) ~ "1999-2003",
                            grepl("_p2_", analysis_title) ~ "2004-2008",
                            grepl("_p3_", analysis_title) ~ "2009-2013",
                            TRUE ~ "999"),
               valuetype = ifelse(grepl("_n_", analysis_title), 'Count', 'Rate')
                ) #%>%
        # group_by(cancer, datatype, year, valuetype) %>%
        # mutate(nflag = str_c("N=", sum(!is.na(prim_cluster)))) %>%
        # ungroup
    return(fctt)    
}



```


```{r ellipse test, include=F, eval=F}
packed = c(37370, 38400, 22310, 22070, 22030, 37380, 37390, 22050, 22040, 22010,
                          38310, 22060, 22020, 38330, 37310, 38370, 38390, 37050, 38030, 37100,
                          37030, 37320, 38320, 38360, 38380, 37360, 38060, 37070, 36060, 38080,
                          37330, 37040, 38340, 38020, 36330, 38010, 38350, 35330, 35340, 35050,
                          33340, 37012, 37400, 37080, 36030, 36020, 37340, 37350, 38070, 38040,
                          38050, 36320, 37020, 37060, 37410, 35320, 38100, 37090, 36350, 37420,
                          36360, 26310, 21120, 38090, 35350, 37011, 33330, 21080, 34310, 21150,
                          36370, 21110, 26010, 35360, 32050, 33380)

satscanres_to_sf(p_v0_resl[[2]], dat1, 0) %>%
    st_geometry %>%
    plot(axes=T)
covar_origin_00_fc %>% filter(sgg_cd_c %in% packed) %>%
    st_centroid %>%
    st_geometry %>%
    plot(add=T, pch=19, col='red')
covar_origin_00_fc %>% #filter(sgg_cd_c %in% packed) %>%
    st_centroid %>%
    st_geometry %>%
    plot(add=T, pch=19, cex=0.3, col='blue')

```




## Data filtering
```{r data filtering}


# lisa_incidence_sf = extr_lisa_sf(covar_origin_00_fc, covar_origin_05_fc, covar_origin_10_fc, "ragest_i_*.*male*")
# lisa_mortality_sf = extr_lisa_sf(covar_origin_00_fc, covar_origin_05_fc, covar_origin_10_fc, "ragest_d_*.*male*")

# save(lisa_incidence_sf, lisa_mortality_sf, file = "/mnt/c/Users/sigma/Documents/LISA_integrated_sf_091522.RData", compress = 'xz', compression_level = 9)

# Reorganize: sets 1-4
sss_incidence_sf_v0 = extr_sss_sf(covar_origin_00_fc, p_v0_resl, "_i_") %>%
    mutate(vset = 'Base')
sss_mortality_sf_v0 = extr_sss_sf(covar_origin_00_fc, p_v0_resl, "_d_") %>%
    mutate(vset = 'Base')
sss_incidence_sf_va = extr_sss_sf(covar_origin_00_fc, p_va_resl, "_i_") %>%
    mutate(vset = 'M1: Base+Senior')
sss_mortality_sf_va = extr_sss_sf(covar_origin_00_fc, p_va_resl, "_d_") %>%
    mutate(vset = 'M1: Base+Senior')
sss_incidence_sf_v1 = extr_sss_sf(covar_origin_00_fc, p_v1_resl, "_i_") %>%
    mutate(vset = 'M2: M1+Education')
sss_mortality_sf_v1 = extr_sss_sf(covar_origin_00_fc, p_v1_resl, "_d_") %>%
    mutate(vset = 'M2: M1+Education')
sss_incidence_sf_v2 = extr_sss_sf(covar_origin_00_fc, p_v2_resl, "_i_") %>%
    mutate(vset = 'M3: M2+Behavior')
sss_mortality_sf_v2 = extr_sss_sf(covar_origin_00_fc, p_v2_resl, "_d_") %>%
    mutate(vset = 'M3: M2+Behavior')
sss_incidence_sf_v3 = extr_sss_sf(covar_origin_00_fc, p_v3_resl, "_i_") %>%
    mutate(vset = 'M4: M3+Environment')
sss_mortality_sf_v3 = extr_sss_sf(covar_origin_00_fc, p_v3_resl, "_d_") %>%
    mutate(vset = 'M4: M3+Environment')
# sss_incidence_sf_v5 = extr_sss_sf(covar_origin_00_fc, p_v3_resl, "_i_") %>%
#     mutate(vset = 'M5: M4+Screening')
# sss_mortality_sf_v5 = extr_sss_sf(covar_origin_00_fc, p_v3_resl, "_d_") %>%
#     mutate(vset = 'M5: M4+Screening')

sss_incidence_df = 
    rbind(sss_incidence_sf_v0,
          sss_incidence_sf_va,
          sss_incidence_sf_v1,
          sss_incidence_sf_v2,
          sss_incidence_sf_v3) %>%
    mutate(sex = ifelse(grepl('_female_', analysis_title), 'Female', 'Male')) %>%
    st_drop_geometry
sss_mortality_df = 
    rbind(sss_mortality_sf_v0,
          sss_mortality_sf_va,
          sss_mortality_sf_v1,
          sss_mortality_sf_v2,
          sss_mortality_sf_v3) %>%
    mutate(sex = ifelse(grepl('_female_', analysis_title), 'Female', 'Male')) %>%
    st_drop_geometry

# TODO: 091522; recheck for the reasonable plots
ref_check = 
    expand.grid(sgg_cd_c = unique(sss_incidence_df$sgg_cd_c),
                vset = c("Base", "M1: Base+Senior", "M2: M1+Education", "M3: M2+Behavior", "M4: M3+Environment"),
                year = c('1999-2003', '2004-2008', '2009-2013'),
                cancer = c('Stomach', 'Lung'),
                sex = c('Male', 'Female')) %>%
    filter(year != "1999-2003" | vset != c("M3: M2+Behavior"))
base_sgg = covar_origin_00_fc %>%
    dplyr::select(sgg_cd_c)

sss_incidence_sf = right_join(base_sgg, ref_check) %>%
    left_join(sss_incidence_df)
sss_mortality_sf = right_join(base_sgg, ref_check) %>%
    left_join(sss_mortality_df)


```

## Lung cancer (male)
```{r Lung (male), fig.width = 12, fig.height = 7.5}
sss_incidence_sf_p = 
    sss_incidence_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Lung" & sex == "Male") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 

sss_mortality_sf_p = 
    sss_mortality_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Lung" & sex == "Male") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 


for (k in seq.int(1, nrow(sss_incidence_sf_p))) {
    sss_incidence_sf_p$geom[[k]] = sss_incidence_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}
for (k in seq.int(1, nrow(sss_mortality_sf_p))) {
    sss_mortality_sf_p$geom[[k]] = sss_mortality_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}


sss_incidence_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Lung" & sex == "Male") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_incidence_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Lung incidence rate\n(male)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))

sss_mortality_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Lung" & sex == "Male") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_mortality_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Lung mortality rate\n(male)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))
```


## Lung cancer (female)
```{r Lung (female), fig.width = 12, fig.height = 7.5, eval=F, include=F}
sss_incidence_sf_p = 
    sss_incidence_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Lung" & sex == "Female") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 

sss_mortality_sf_p = 
    sss_mortality_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Lung" & sex == "Female") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 


for (k in seq.int(1, nrow(sss_incidence_sf_p))) {
    sss_incidence_sf_p$geom[[k]] = sss_incidence_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}
for (k in seq.int(1, nrow(sss_mortality_sf_p))) {
    sss_mortality_sf_p$geom[[k]] = sss_mortality_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}

sss_incidence_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Lung" & sex == "Female") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_incidence_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Lung incidence rate\n(female)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))

sss_mortality_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Lung" & sex == "Female") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_mortality_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Lung mortality rate\n(female)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))
```


## Stomach cancer (male)
```{r Stomach (male), fig.width = 12, fig.height = 7.5}
sss_incidence_sf_p = 
    sss_incidence_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Stomach" & sex == "Male") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 

sss_mortality_sf_p = 
    sss_mortality_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Stomach" & sex == "Male") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 


for (k in seq.int(1, nrow(sss_incidence_sf_p))) {
    sss_incidence_sf_p$geom[[k]] = sss_incidence_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}
for (k in seq.int(1, nrow(sss_mortality_sf_p))) {
    sss_mortality_sf_p$geom[[k]] = sss_mortality_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}

sss_incidence_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Stomach" & sex == "Male") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_incidence_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Stomach incidence rate\n(male)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))

sss_mortality_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Stomach" & sex == "Male") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_mortality_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Stomach mortality rate\n(male)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))
```

## Stomach cancer (female)
```{r Stomach (female), fig.width = 12, fig.height = 7.5}
sss_incidence_sf_p = 
    sss_incidence_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Stomach" & sex == "Female") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 

sss_mortality_sf_p = 
    sss_mortality_sf %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
        filter(cancer == "Stomach" & sex == "Female") %>%
        group_by(cancer, sex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 


for (k in seq.int(1, nrow(sss_incidence_sf_p))) {
    sss_incidence_sf_p$geom[[k]] = sss_incidence_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}
for (k in seq.int(1, nrow(sss_mortality_sf_p))) {
    sss_mortality_sf_p$geom[[k]] = sss_mortality_sf_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}

sss_incidence_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Stomach" & sex == "Female") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_incidence_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Stomach incidence rate\n(female)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))

sss_mortality_sf %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster)) %>%
    filter(cancer == "Stomach" & sex == "Female") %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_shape(sss_mortality_sf_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "vset"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Stomach mortality rate\n(female)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))
```

# Sensitivity analysis
## Sensitivity (LISA)
```{r LISA plot, fig.width = 7.8, fig.height = 6}
lisa_incidence_sf = extr_lisa_sf(covar_origin_00_fc, covar_origin_05_fc, covar_origin_10_fc, "ragest_i_*.*male*")
lisa_mortality_sf = extr_lisa_sf(covar_origin_00_fc, covar_origin_05_fc, covar_origin_10_fc, "ragest_d_*.*male*")
# load(str_c(rdsdir, "Output/LISA_integrated_sf_091522.RData"))
colpal = c("#4E79A7", "deepskyblue1", "pink", "#E15759")
colpal = rev(colpal)
namepal = c("HH", "HL", "LH", "LL")

lisa_incidence_sf = lisa_incidence_sf %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020))
lisa_mortality_sf = lisa_mortality_sf %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020))
levels_cancersex = c("Lung (Male)", "Stomach (Male)", "Stomach (Female)")

lisa_incidence_sf %>%
    filter(cancer != "Lung" | !grepl('_female_', analysis_title)) %>%
    mutate(cancersex = ifelse(grepl("_male_", analysis_title), str_c(cancer, " (Male)"), str_c(cancer, " (Female)"))) %>%
    mutate(cancersex = factor(cancersex, levels = levels_cancersex)) %>%
    # filter(!(cancer == "Lung" & grepl('(female)', analysis_title))) %>%
    tm_shape(.) +
        tm_fill('LISA', title = "Local Moran's I", pal = colpal, showNA = FALSE, colorNA = "white", labels = namepal) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "cancersex"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))


lisa_mortality_sf %>%
    filter(cancer != "Lung" | !grepl('_female_', analysis_title)) %>%
    mutate(cancersex = ifelse(grepl("_male_", analysis_title), str_c(cancer, " (Male)"), str_c(cancer, " (Female)"))) %>%
    mutate(cancersex = factor(cancersex, levels = levels_cancersex)) %>%
    # filter(!(cancer == "Lung" & grepl('(female)', analysis_title))) %>%
    tm_shape(.) +
        tm_fill('LISA', title = "Local Moran's I", pal = colpal, showNA = FALSE, colorNA = "white", labels = namepal) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "cancersex"), nrow = 3, ncol = 4) +
        tm_layout(panel.label.bg.color = 'transparent',
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))



```

## Sensitivity (Poisson)

```{r sensitivity plot Poisson, fig.width = 7.8, fig.height = 6}

p_v0_reslp = clear_input(filepath = str_c(rdsdir, "satscan_NPois_uncontrolled_resid.rds"))
p_va_reslp = clear_input(filepath = str_c(rdsdir, "satscan_NPois_age_resid.rds"))
# p_v1_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset1_resid.rds"))
# p_v2_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset2_resid.rds"))
# p_v3_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset3_resid.rds"))
# p_v4_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_vset4_resid.rds"))

sssp_incidence_sf_v0 = extr_sss_sf(covar_origin_00_fc, p_v0_reslp, "_i_") %>%
    mutate(vset = 'Base') %>%
    mutate(sex = ifelse(grepl('_female_', analysis_title), 'Female', 'Male'))
sssp_mortality_sf_v0 = extr_sss_sf(covar_origin_00_fc, p_v0_reslp, "_d_") %>%
    mutate(vset = 'Base') %>%
    mutate(sex = ifelse(grepl('_female_', analysis_title), 'Female', 'Male'))
sssp_incidence_df_va = extr_sss_sf(covar_origin_00_fc, p_va_reslp, "_i_") %>%
    mutate(vset = 'M1: Base+Senior') %>%
    mutate(sex = ifelse(grepl('_female_', analysis_title), 'Female', 'Male')) %>%
    st_drop_geometry
sssp_mortality_df_va = extr_sss_sf(covar_origin_00_fc, p_va_reslp, "_d_") %>%
    mutate(vset = 'M1: Base+Senior') %>%
    mutate(sex = ifelse(grepl('_female_', analysis_title), 'Female', 'Male')) %>%
    st_drop_geometry

# sssp_incidence_df_va = right_join(sssp_incidence_sf_va, ref_check)
# sssp_mortality_df_va = right_join(sssp_mortality_sf_va, ref_check)

ref_check_m1 = ref_check %>%
    filter(grepl('^M1', vset))

sssp_incidence_sf_va = right_join(base_sgg, ref_check_m1) %>%
    left_join(sssp_incidence_df_va)
sssp_mortality_sf_va = right_join(base_sgg, ref_check_m1) %>%
    left_join(sssp_mortality_df_va)

# sssp_incidence_sf_vad = 
# sssp_incidence_sf_va %>%
#     mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, prim_cluster))

sssp_incidence_sf_va_p = 
    sssp_incidence_sf_va %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, 'Detected')) %>%
        filter(sex != "Female" | cancer != "Lung") %>%
        mutate(cancersex = ifelse(sex == "Male", str_c(cancer, " (Male)"), str_c(cancer, " (Female)"))) %>%
        group_by(cancer, sex, cancersex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 

sssp_mortality_sf_va_p = 
    sssp_mortality_sf_va %>%
        mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, 'Detected')) %>%
        filter(sex != "Female" | cancer != "Lung") %>%
        mutate(cancersex = ifelse(sex == "Male", str_c(cancer, " (Male)"), str_c(cancer, " (Female)"))) %>%
        group_by(cancer, sex, cancersex, year, vset) %>%
        summarize(nflag = unique(nflag)) %>%
        ungroup %>%
        st_centroid 


for (k in seq.int(1, nrow(sssp_incidence_sf_va_p))) {
    sssp_incidence_sf_va_p$geom[[k]] = sssp_incidence_sf_va_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}
for (k in seq.int(1, nrow(sssp_mortality_sf_va_p))) {
    sssp_mortality_sf_va_p$geom[[k]] = sssp_mortality_sf_va_p$geom[[k]] + st_point(c(-1.35e5, 2e5), dim = 'XY')    
}


sssp_incidence_sf_va %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, 'Detected')) %>%
    filter(sex != "Female" | cancer != "Lung") %>%
    mutate(cancersex = ifelse(sex == "Male", str_c(cancer, " (Male)"), str_c(cancer, " (Female)"))) %>%
    # filter((cancer != "Lung" | sex != "Female")) %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "cancersex"), nrow = 3, ncol = 3) +
        tm_shape(sssp_incidence_sf_va_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "cancersex"), nrow = 3, ncol = 3) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Incidence count\n(Base+Senior)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))

sssp_mortality_sf_va %>%
    mutate(prim_cluster = ifelse(prim_cluster == "FALSE", NA, "Detected")) %>%
    filter(sex != "Female" | cancer != "Lung") %>%
    mutate(cancersex = ifelse(sex == "Male", str_c(cancer, " (Male)"), str_c(cancer, " (Female)"))) %>%
    # filter((cancer != "Lung" | sex != "Female")) %>%
    tm_shape(.) +
        tm_fill('prim_cluster', title = "Primary cluster", pal = c("#E15759"), showNA = FALSE, colorNA = "white", labels = c('Detected')) +
        tm_borders('dark grey', lwd = 0.4) +
        tm_facets(by = c("year", "cancersex"), nrow = 3, ncol = 3) +
        tm_shape(sssp_mortality_sf_va_p) +
        tm_text("nflag", size = 1.5, remove.overlap = TRUE) +
        tm_facets(by = c("year", "cancersex"), nrow = 3, ncol = 3) +
        tm_layout(panel.label.bg.color = 'transparent',
                  title = "Mortality count\n(Base+Senior)",
                  frame = FALSE,
                  legend.title.size = 1,
                  legend.text.size = 1,
                  panel.label.size = 1.4,
                  fontfamily = "Pretendard",
                  outer.margins = c(0.005, 0.005, 0.005, -0.05))

```


## summary tables
```{r summary tables, eval=F, include=F}
cns_s1 = c('sgg_cd_c', 'n_p_male_1', 'n_p_female_1', 'n_i_Lung_male_1', 'n_i_Lung_female_1', 'n_i_Stomach_male_1', 'n_i_Stomach_female_1', 'ragest_i_Lung_male_1', 'ragest_i_Lung_female_1', 'ragest_i_Stomach_male_1', 'ragest_i_Stomach_female_1', 'n_d_Lung_male_1', 'n_d_Lung_female_1', 'n_d_Stomach_male_1', 'n_d_Stomach_female_1', 'ragest_d_Lung_male_1', 'ragest_d_Lung_female_1', 'ragest_d_Stomach_male_1', 'ragest_d_Stomach_female_1', 'p_hbac_male', 'p_hbac_female', 'p_65p_male', 'p_65p_female', 'ap_sum_em_co', 'ap_sum_em_nox', 'ap_sum_em_sox', 'ap_sum_em_tsp', 'ap_sum_em_pm10', 'ap_sum_em_voc', 'ap_sum_em_nh3', 'ap_PM10_pred', 'ap_NO2_pred', 'NDVI_mean')
cns_s2 = c('sgg_cd_c', 'n_p_male_2', 'n_p_female_2', 'n_i_Lung_male_2', 'n_i_Lung_female_2', 'n_i_Stomach_male_2', 'n_i_Stomach_female_2', 'ragest_i_Lung_male_2', 'ragest_i_Lung_female_2', 'ragest_i_Stomach_male_2', 'ragest_i_Stomach_female_2', 'n_d_Lung_male_2', 'n_d_Lung_female_2', 'n_d_Stomach_male_2', 'n_d_Stomach_female_2', 'ragest_d_Lung_male_2', 'ragest_d_Lung_female_2', 'ragest_d_Stomach_male_2', 'ragest_d_Stomach_female_2', 'p_hbac_male', 'p_hbac_female', 'p_65p_male', 'p_65p_female', 'ap_sum_em_co', 'ap_sum_em_nox', 'ap_sum_em_sox', 'ap_sum_em_tsp', 'ap_sum_em_pm10', 'ap_sum_em_voc', 'ap_sum_em_nh3', 'ap_PM10_pred', 'ap_NO2_pred', 'NDVI_mean')
cns_s3 = c('sgg_cd_c', 'n_p_male_3', 'n_p_female_3', 'n_i_Lung_male_3', 'n_i_Lung_female_3', 'n_i_Stomach_male_3', 'n_i_Stomach_female_3', 'ragest_i_Lung_male_3', 'ragest_i_Lung_female_3', 'ragest_i_Stomach_male_3', 'ragest_i_Stomach_female_3', 'n_d_Lung_male_3', 'n_d_Lung_female_3', 'n_d_Stomach_male_3', 'n_d_Stomach_female_3', 'ragest_d_Lung_male_3', 'ragest_d_Lung_female_3', 'ragest_d_Stomach_male_3', 'ragest_d_Stomach_female_3', 'p_hbac_male', 'p_hbac_female', 'p_65p_male', 'p_65p_female', 'ap_sum_em_co', 'ap_sum_em_nox', 'ap_sum_em_sox', 'ap_sum_em_tsp', 'ap_sum_em_pm10', 'ap_sum_em_voc', 'ap_sum_em_nh3', 'ap_PM10_pred', 'ap_NO2_pred', 'NDVI_mean')

# covar_origin_00_fc %>% st_drop_geometry %>% summarize_at(.vars = vars(all_of(cns_s1[-1])), .funs = list('min'=min, 'median'=median, 'mean'=mean, 'max'=max, 'sd'=sd)) %>% ungroup %>% pivot_longer(cols = 1:ncol(.)) %>% mutate(value = map_dfr(value, ~as.data.frame(matrix(., nrow=1)))) %>% unnest#mutate(statx = as.vector(str_extract_all(name, "_(min|mean|median|max|sd)", simplify = T)[1]), variable = as.vector(str_replace(name, "_(min|mean|median|max|sd)", ""))) %>% dplyr::select(-name) %>% pivot_wider(names_from = statx, values_from = value)
covar_origin_00_fc %>% st_drop_geometry %>% 
    dplyr::select(all_of(cns_s1[-1])) %>% 
    psych::describe(fast=T) %>% round(., 1) %>% 
    as.data.frame %>% 
    dplyr::select(all_of(c('min', 'mean', 'max', 'sd'))) %>% 
    write.csv(str_c(rdsdir, "Manuscript/Table3_1.csv"))

covar_origin_05_fc %>% st_drop_geometry %>% 
    dplyr::select(all_of(cns_s2[-1])) %>% 
    psych::describe(fast=T) %>% round(., 1) %>% 
    as.data.frame %>% 
    dplyr::select(all_of(c('min', 'mean', 'max', 'sd'))) %>% 
    write.csv(str_c(rdsdir, "Manuscript/Table3_2.csv"))

covar_origin_10_fc %>% st_drop_geometry %>% 
    dplyr::select(all_of(cns_s3[-1])) %>% 
    psych::describe(fast=T) %>% round(., 1) %>% 
    as.data.frame %>% 
    dplyr::select(all_of(c('min', 'mean', 'max', 'sd'))) %>% 
    write.csv(str_c(rdsdir, "Manuscript/Table3_3.csv"))


covar_origin_05_fc %>%
    filter(n_d_Stomach_male_2 == 0)



mapsf::mf_typo(covar_origin_05_fc %>% mutate(n_d_Stomach_male_2i = ifelse(n_d_Stomach_male_2 == 0, TRUE, FALSE)), 'n_d_Stomach_male_2i')
mapsf::mf_typo(covar_origin_10_fc %>% mutate(n_i_Lung_male_3i = ifelse(n_d_Lung_male_3 == 0, TRUE, FALSE)), 'n_i_Lung_male_3i')
mapsf::mf_typo(covar_origin_10_fc %>% mutate(n_i_Stomach_male_3i = ifelse(n_i_Stomach_male_3 == 0, TRUE, FALSE)), 'n_i_Stomach_male_3i')

```