---
title: "Stomach and lung cancer incidence/mortality clustering results"
author: "Insang Song"
date: 08-26-2022
theme: "spacelab"
format: 
  html:
    toc: true
    self-contained: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

- General description
    - This document includes all the LISA (aka Local Moran's _I_) maps in South Korea at district level.
    - Ongjin, Ulleung, Jeju, and Seogwipo were excluded.
    - We used the age-standardized mortality/incidence rates in the data
        - For the district unification, we calculated population-weight-averaged rates in any districts that were subject to the calculation.

- Change log
    - 07/14/2022
        - Updated data


```{r}
source('../Base/base_functions.R')
options(repos = 'https://cran.seoul.go.kr')
if (!require(pacman)) { install.packages('pacman') } 

p_load(tidyverse, sf, stars, raster, starsExtra, readxl, here, tmap, stargazer, smerc, DClusterm, kableExtra, patchwork, rmapshaper, spdep)

username = 'sigma'
basedir = sprintf('/mnt/c/Users/%s/', username)
rdatafiles = list.files(path = str_c(basedir, 'Documents/GP/'), pattern = '*.RData', full.names = TRUE)
geopath = str_c(basedir, "OneDrive/Data/Korea/")
drive = str_c(basedir, "OneDrive/NCC_Project/CancerClustering/")
geopath = str_c(basedir, "OneDrive/Data/Korea/")
dbdir = drive  
rdsdir = sprintf("/mnt/c/Users/%s/OneDrive/NCC_Project/CancerClustering/", username)

```


```{r}
load(str_c(drive, '/Manuscript/Clustering_Base_sf_062422.RData'))

covar_origin_10_fc = covar_origin_10_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.125, keep_shapes = TRUE)
covar_origin_05_fc = covar_origin_05_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.125, keep_shapes = TRUE)
covar_origin_00_fc = covar_origin_00_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.125, keep_shapes = TRUE)

clear_input = function(filepath, alpha = 0.01, locmin = 2) {
    # alpha: significance level
    # locmin: how many points should be included at least?
    res = read_rds(filepath)
    labels = as.data.frame(str_split_fixed(res$analysis_title, "_", 6))
    colnames(labels) = c("cancertype", "period", "measure", "target", "sex", "vset")
    res = res %>%
          bind_cols(labels, .) %>%
          filter(pvalue <= alpha & number_locs >= locmin)
    resl = res %>% split(., .$analysis_title)
    return(resl)
}

p_v0_resl = clear_input(filepath = str_c(rdsdir, "satscan_ASMR_uncontrolled_resid.rds"))

```

# Overview
- Incidence and mortality rates: (Sum of cases) / (Sum of the population)
- All inclusive variables
    - Set 1: elderly population rate (%) and higher than bachelor's degree (%)
    - Set 2: Set 1 + including emission, residential exposure, and NDVI
    - Set 3: for periods 2 and 3. All but insurance premium and stomach cancer screening
    - Set 4: for period 3 only. All variables.

# Lung Cancer
## Incidence
```{r Lung cancer cluster plots (incidence), fig.width=12, fig.height = 5.6}

tmap::tmap_arrange(
    map_lisa(covar_origin_00_fc, "ragest_i_Lung_male_1") +
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_05_fc, "ragest_i_Lung_male_2") +
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_10_fc, "ragest_i_Lung_male_3") +
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Male, LISA)   ', frame = FALSE),
    ncol = 3)
tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Lung_p1_i_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Lung_p2_i_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Lung_p3_i_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Male, SaTScan)', frame = FALSE),
    ncol = 3)


```


## Mortality
```{r Lung cancer cluster plots (mortality), fig.width=12, fig.height = 5.6}

tmap::tmap_arrange(
    map_lisa(covar_origin_00_fc, "ragest_d_Lung_male_1") +
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_05_fc, "ragest_d_Lung_male_2") +
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_10_fc, "ragest_d_Lung_male_3") +
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Male, LISA)   ', frame = FALSE),
    ncol = 3)
tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Lung_p1_d_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Lung_p2_d_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Lung_p3_d_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Male, SaTScan)', frame = FALSE),
    ncol = 3)


```




# Stomach Cancer
## Incidence
```{r Stomach cancer cluster plots (incidence), fig.width=12, fig.height = 5.6}

tmap::tmap_arrange(
    map_lisa(covar_origin_00_fc, "ragest_i_Stomach_female_1") +
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Female, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_05_fc, "ragest_i_Stomach_female_2") +
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Female, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_10_fc, "ragest_i_Stomach_female_3") +
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Female, LISA)   ', frame = FALSE),
    ncol = 3)
tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_i_ragest_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Female, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_i_ragest_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Female, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_i_ragest_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Female, SaTScan)', frame = FALSE),
    ncol = 3)

tmap::tmap_arrange(
    map_lisa(covar_origin_00_fc, "ragest_i_Stomach_male_1") +
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_05_fc, "ragest_i_Stomach_male_2") +
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_10_fc, "ragest_i_Stomach_male_3") +
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Male, LISA)   ', frame = FALSE),
    ncol = 3)
tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_i_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_i_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_i_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Male, SaTScan)', frame = FALSE),
    ncol = 3)


```


## Mortality
```{r Stomach cancer cluster plots (mortality), fig.width=12, fig.height = 5.6}

tmap::tmap_arrange(
    map_lisa(covar_origin_00_fc, "ragest_d_Stomach_female_1") +
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Female, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_05_fc, "ragest_d_Stomach_female_2") +
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Female, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_10_fc, "ragest_d_Stomach_female_3") +
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Female, LISA)   ', frame = FALSE),
    ncol = 3)
tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_d_ragest_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Female, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_d_ragest_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Female, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_d_ragest_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Female, SaTScan)', frame = FALSE),
    ncol = 3)

tmap::tmap_arrange(
    map_lisa(covar_origin_00_fc, "ragest_d_Stomach_male_1") +
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_05_fc, "ragest_d_Stomach_male_2") +
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Male, LISA)   ', frame = FALSE),
    map_lisa(covar_origin_10_fc, "ragest_d_Stomach_male_3") +
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Male, LISA)   ', frame = FALSE),
    ncol = 3)
tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_d_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_d_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Male, SaTScan)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_d_ragest_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Male, SaTScan)', frame = FALSE),
    ncol = 3)


```

