---
title: "Stomach and lung cancer incidence/mortality clustering results (Poisson)"
author: "Insang Song"
date: 08-30-2022
theme: "spacelab"
format: 
  html:
    toc: true
    self-contained: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Change log

- 02/12/2022
    - The default value of `alpha` in the package we use was 0.1; this documents is based on `alpha=0.05`.
    - Primary cluster (most significant cluster) has darker color (i.e., dark red)
    
- 02/17/2022    
    - Variable sets 3 and 4 were applied
    - TODO: exclude isles and run period 3 analysis with available explanatory factors

- 03/16/2022
    - Excluded isles (Ulleung, Ongjin)
    - `ubpop` from 0.5 to 0.35, `alpha` from 0.05 to 0.01

- 04/23/2022
    - Switched to SaTScan
    - All periods & covariate controls

- 04/28/2022
    - Residuals (normal model)

- 05/19/2022
    - Excluding Jeju and Seogwipo
    - Gini-optimized clusters

- 06/17/2022
    - Excluded all-sex cases
    - Weighted normal model using the number of cases
    - Gini-optimization is not available for weighted normal models

- 06/22/2022
    - Fixed the case and population parameter settings in SaTScan software

- 06/24/2022
    - Fixed data aggregation errors
    - Redo analysis

- 06/25/2022
    - For covariate controlled models, the weighted normal model will not be applied
    - The maximum cluster size (no matter it is subject to "reported" or "generally analyzed" configuration) does not work in weighted normal models; The maximum percentage of spatial units is now set 35% 
    - `alpha` reset to 0.05

- 08/02/2022
    - Poisson model

- 08/06/2022
    - Poisson model (age controlled)

```{r}
source('./Base/base_functions.R')
options(repos = 'https://cran.seoul.go.kr')
if (!require(pacman)) { install.packages('pacman') } 

p_load(tidyverse, sf, tmap, stargazer, smerc, DClusterm, kableExtra, patchwork, rmapshaper, spdep)

username = 'sigma'
basedir = sprintf('/mnt/c/Users/%s/', username)
rdatafiles = list.files(path = str_c(basedir, 'Documents/GP/'), pattern = '*.RData', full.names = TRUE)
geopath = str_c(basedir, "OneDrive/Data/Korea/")
drive = str_c(basedir, "OneDrive/NCC_Project/CancerClustering/")
geopath = str_c(basedir, "OneDrive/Data/Korea/")
dbdir = drive  
rdsdir = drive#sprintf("/mnt/c/Users/%s/OneDrive/NCC_Project/CancerClustering/", username)

```




```{r}
load(str_c(drive, '/Manuscript/Clustering_Base_sf_062422.RData'))

covar_origin_10_fc = covar_origin_10_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.05, keep_shapes = TRUE)
covar_origin_05_fc = covar_origin_05_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.05, keep_shapes = TRUE)
covar_origin_00_fc = covar_origin_00_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430, 39010, 39020)) %>%
    ms_simplify(keep = 0.05, keep_shapes = TRUE)

clear_input = function(filepath, alpha = 0.05, locmin = 2) {
    # alpha: significance level
    # locmin: how many points should be included at least?
    res = read_rds(filepath)
    labels = as.data.frame(str_split_fixed(res$analysis_title, "_", 6))
    colnames(labels) = c("cancertype", "period", "measure", "target", "sex", "vset")
    res = res %>%
          bind_cols(labels, .) %>%
          filter(pvalue <= alpha & number_locs >= locmin)
    resl = res %>% split(., .$analysis_title)
    return(resl)
}

clear_satscan_df = function(filepath, alpha = 0.05, locmin = 2) {
    # alpha: significance level
    # locmin: how many points should be included at least?
    res = read_rds(filepath)
    labels = as.data.frame(str_split_fixed(res$analysis_title, "_", 6))
    colnames(labels) = c("cancertype", "period", "measure", "target", "sex", "vset")
    res = res %>%
          bind_cols(labels, .) %>%
          filter(number_locs >= locmin)
    return(res)
}



p_v0_resl = clear_input(filepath = str_c(rdsdir, "satscan_NPois_uncontrolled_resid.rds"))
p_va_resl = clear_input(filepath = str_c(rdsdir, "satscan_NPois_age_resid.rds"))
p_v1_resl = clear_input(filepath = str_c(rdsdir, "satscan_NPois_vset1_resid.rds"))
p_v2_resl = clear_input(filepath = str_c(rdsdir, "satscan_NPois_vset2_resid.rds"))
p_v3_resl = clear_input(filepath = str_c(rdsdir, "satscan_NPois_vset3_resid.rds"))
p_v4_resl = clear_input(filepath = str_c(rdsdir, "satscan_NPois_vset4_resid.rds"))


```

```{r include=FALSE, eval=FALSE}
p_v0_resdf = clear_satscan_df(filepath = str_c(rdsdir, "satscan_ASMR_uncontrolled_resid.rds"))
p_v1_resdf = clear_satscan_df(filepath = str_c(rdsdir, "satscan_ASMR_vset1_resid.rds"))
p_v2_resdf = clear_satscan_df(filepath = str_c(rdsdir, "satscan_ASMR_vset2_resid.rds"))
p_v3_resdf = clear_satscan_df(filepath = str_c(rdsdir, "satscan_ASMR_vset3_resid.rds"))
p_v4_resdf = clear_satscan_df(filepath = str_c(rdsdir, "satscan_ASMR_vset4_resid.rds"))


```
```{r include=FALSE, eval=FALSE}
make_shortdf = function(sfd) {
    sfd_d =
        sfd %>%
        dplyr::select(sgg_cd_c, matches('^ragest*.*Lung_male.*|^ragest*.*_Stomach_(male|female).*')) %>%
        st_drop_geometry %>%
        pivot_longer(cols = 2:ncol(.))
    labelsc = as.data.frame(str_split_fixed(sfd_d$name, "_", 5))
    colnames(labelsc) = c("measure", "target", "cancertype", "sex", "period")
    sfd_d = bind_cols(sfd_d, labelsc)
    return(sfd_d)
}

make_shortdf2 = function(sfd) {
    sfd_d =
        sfd %>%
        dplyr::select(sgg_cd_c, matches('^n*.*Lung_male.*|^n*.*_Stomach_(male|female).*')) %>%
        st_drop_geometry %>%
        pivot_longer(cols = 2:ncol(.))
    labelsc = as.data.frame(str_split_fixed(sfd_d$name, "_", 5))
    colnames(labelsc) = c("measure", "target", "cancertype", "sex", "period")
    sfd_d = bind_cols(sfd_d, labelsc)
    return(sfd_d)
}

c10 = make_shortdf(covar_origin_10_fc)
c05 = make_shortdf(covar_origin_05_fc)
c00 = make_shortdf(covar_origin_00_fc)

c10_gg = c10 %>%
    ggplot(data = ., mapping = aes(x = value)) +
    theme_bw() +
    geom_histogram(bins = 50) +
    facet_wrap(target * cancertype ~ sex) 
c05_gg = c05 %>%
    ggplot(data = ., mapping = aes(x = value)) +
    theme_bw() +
    geom_histogram(bins = 50) +
    facet_wrap(target * cancertype ~ sex) 
c00_gg = c00 %>%
    ggplot(data = ., mapping = aes(x = value)) +
    theme_bw() +
    geom_histogram(bins = 50) +
    facet_wrap(target * cancertype ~ sex) 

c10n = make_shortdf2(covar_origin_10_fc)
c05n = make_shortdf2(covar_origin_05_fc)
c00n = make_shortdf2(covar_origin_00_fc)

c10n_gg = c10n %>%
    ggplot(data = ., mapping = aes(x = value)) +
    theme_bw() +
    geom_histogram(bins = 50) +
    facet_wrap(target * cancertype ~ sex) 
c05n_gg = c05n %>%
    ggplot(data = ., mapping = aes(x = value)) +
    theme_bw() +
    geom_histogram(bins = 50) +
    facet_wrap(target * cancertype ~ sex) 
c00n_gg = c00n %>%
    ggplot(data = ., mapping = aes(x = value)) +
    theme_bw() +
    geom_histogram(bins = 50) +
    facet_wrap(target * cancertype ~ sex) 


```


# Overview
- All inclusive variables
    - Set a: Age only (elderly population rate, %)
    - Set 1: elderly population rate (%) and higher than bachelor's degree (%)
    - Set 2: Set 1 + including emission, residential exposure, and NDVI
    - Set 3: for periods 2 and 3. All but insurance premium and stomach cancer screening
    - Set 4: for period 3 only. All variables.

# Lung Cancer
```{r Lung cancer cluster plots, fig.width=12, fig.height = 5.6, eval = FALSE}

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Lung_p1_i_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer incidence count\n(1999-2003, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Lung_p2_i_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer incidence count\n(2004-2008, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Lung_p3_i_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer incidence count\n(2009-2013, Male, Uncontrolled)', frame = FALSE), ncol=3)

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_va_resl[["Lung_p1_i_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer incidence count\n(1999-2003, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_va_resl[["Lung_p2_i_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer incidence count\n(2004-2008, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_va_resl[["Lung_p3_i_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer incidence count\n(2009-2013, Male, age variable)', frame = FALSE), ncol=3)


tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Lung_p1_d_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer mortality count\n(1999-2003, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Lung_p2_d_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer mortality count\n(2004-2008, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Lung_p3_d_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Lung cancer mortality count\n(2009-2013, Male, Uncontrolled)', frame = FALSE), ncol=3)


tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_va_resl[["Lung_p1_d_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(1999-2003, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_va_resl[["Lung_p2_d_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2004-2008, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_va_resl[["Lung_p3_d_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2009-2013, Male, age variable)', frame = FALSE), ncol=3)

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v1_resl[["Lung_p1_d_n_male_v1"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(1999-2003, Male, set 1)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v1_resl[["Lung_p2_d_n_male_v1"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2004-2008, Male, set 1)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v1_resl[["Lung_p3_d_n_male_v1"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2009-2013, Male, set 1)', frame = FALSE), ncol=3)

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v2_resl[["Lung_p1_d_n_male_v2"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(1999-2003, Male, set 2)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v2_resl[["Lung_p2_d_n_male_v2"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2004-2008, Male, set 2)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v2_resl[["Lung_p3_d_n_male_v2"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2009-2013, Male, set 2)', frame = FALSE), ncol=3)

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v3_resl[["Lung_p1_d_n_male_v3"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(1999-2003, Male, set 3)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v3_resl[["Lung_p2_d_n_male_v3"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2004-2008, Male, set 3)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v3_resl[["Lung_p3_d_n_male_v3"]], area = TRUE) + 
            tm_layout(title = 'Lung cancer mortality count\n(2009-2013, Male, set 3)', frame = FALSE), ncol=3)


```

```{r stomach: sex stratified, fig.width=12, fig.height = 5.6, eval = FALSE}

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_i_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence count\n(1999-2003, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_i_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence count\n(2004-2008, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_i_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence count\n(2009-2013, Male, Uncontrolled)', frame = FALSE), ncol=3)

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_va_resl[["Stomach_p1_i_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer incidence count\n(1999-2003, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_va_resl[["Stomach_p2_i_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer incidence count\n(2004-2008, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_va_resl[["Stomach_p3_i_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer incidence count\n(2009-2013, Male, age variable)', frame = FALSE), ncol=3)


tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_d_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality count\n(1999-2003, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_d_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality count\n(2004-2008, Male, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_d_n_male_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality count\n(2009-2013, Male, Uncontrolled)', frame = FALSE), ncol=3)


tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_va_resl[["Stomach_p1_d_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer mortality count\n(1999-2003, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_va_resl[["Stomach_p2_d_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer mortality count\n(2004-2008, Male, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_va_resl[["Stomach_p3_d_n_male_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer mortality count\n(2009-2013, Male, age variable)', frame = FALSE), 
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_i_n_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence count\n(1999-2003, Female, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_i_n_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence count\n(2004-2008, Female, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_i_n_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence count\n(2009-2013, Female, Uncontrolled)', frame = FALSE), ncol=3)

tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_va_resl[["Stomach_p1_i_n_female_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer incidence count\n(1999-2003, Female, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_va_resl[["Stomach_p2_i_n_female_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer incidence count\n(2004-2008, Female, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_va_resl[["Stomach_p3_i_n_female_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer incidence count\n(2009-2013, Female, age variable)', frame = FALSE), ncol=3)


tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_v0_resl[["Stomach_p1_d_n_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality count\n(1999-2003, Female, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_v0_resl[["Stomach_p2_d_n_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality count\n(2004-2008, Female, Uncontrolled)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_v0_resl[["Stomach_p3_d_n_female_"]], area = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality count\n(2009-2013, Female, Uncontrolled)', frame = FALSE), ncol=3)


tmap::tmap_arrange(
    tmap_satscan(covar_origin_00_fc, p_va_resl[["Stomach_p1_d_n_female_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer mortality count\n(1999-2003, Female, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_05_fc, p_va_resl[["Stomach_p2_d_n_female_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer mortality count\n(2004-2008, Female, age variable)', frame = FALSE),
    tmap_satscan(covar_origin_10_fc, p_va_resl[["Stomach_p3_d_n_female_va"]], area = TRUE) + 
            tm_layout(title = 'Stomach cancer mortality count\n(2009-2013, Female, age variable)', frame = FALSE), ncol=3)


```
