---
title: "Stomach and lung cancer incidence/mortality clustering results"
author: "Insang Song"
date: 03-16-2022
theme: "spacelab"
output:
  html_document:
    toc: true
    fig_caption: true
---

```{r}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Change log

- 02/12/2022
    - The default value of `alpha` in the package we use was 0.1; this documents is based on `alpha=0.05`.
    - Primary cluster (most significant cluster) has darker color (i.e., dark red)
    
- 02/17/2022    
    - Variable sets 3 and 4 were applied
    - TODO: exclude isles and run period 3 analysis with available explanatory factors

- 03/16/2022
    - Excluded isles (Ulleung, Ongjin)
    - `ubpop` from 0.5 to 0.35, `alpha` from 0.05 to 0.01

```{r}
source('./base_functions.R')
options(repos = 'https://cran.seoul.go.kr')
if (!require(pacman)) { install.packages('pacman') } 

p_load(tidyverse, sf, stars, raster, starsExtra, readxl, here, tmap, stargazer, smerc, DClusterm, kableExtra, patchwork, rmapshaper)

username = 'sigma'
basedir = sprintf('/mnt/c/Users/%s/', username)
rdatafiles = list.files(path = str_c(basedir, 'Documents/GP/'), pattern = '*.RData', full.names = TRUE)
geopath = str_c(basedir, "OneDrive/Data/Korea/")
#homedir <- "/home/felix/"
drive = str_c(basedir, "OneDrive/NCC_Project/CancerClustering/")
geopath = str_c(basedir, "OneDrive/Data/Korea/")
dbdir = drive  # here::here()

```


```{r data munging, include = FALSE}
# incidence
inc <- read.csv(paste(drive, "cancerInc_sgg.csv", sep = ""), fileEncoding = "EUC-KR")
mor_to <- read.csv(paste(drive, "cancerMor_sgg_total.csv", sep = ""), fileEncoding = "EUC-KR")
mor_me <- read.csv(paste(drive, "cancerMor_sgg_male.csv", sep = ""), fileEncoding = "EUC-KR")
mor_fe <- read.csv(paste(drive, "cancerMor_sgg_female.csv", sep = ""), fileEncoding = "EUC-KR")

conv_table = read.csv(paste(geopath, 'SGG_1995_2018_Conversion_Table_201108.csv', sep = ''), fileEncoding = 'EUC-KR')
# total population for the expected values
# sex code: 0(all), 1(male), 2(female)
pop <- read.csv(paste(drive, "Midyear_Population_1998_2019.csv", sep = ""), fileEncoding = "UTF-8") %>%
    mutate(
        sex0 = plyr::mapvalues(sex0, c(0, 1, 2), c("T", "M", "F")),
        sex_e = plyr::mapvalues(sex0, c("T", "M", "F"), c("Total", "Male", "Female")),
        population = as.numeric(population)
    )
pop_wide = pop %>%
    pivot_wider(names_from = c("sex0", "year"), values_from = population)

colnames(inc) <- c("sex0", "sex", "cancer_type0", "cancer_type", "sgg_cd", "sgg_nm", "year0", "year", "inc0", "type_inc", "unit", "n", "x")
colnames(mor_to) <- c("cause0", "cause", "sgg_cd", "sgg_nm", "sex0", "sex", "type0", "type", "unit", paste("Y", 1998:2019, sep = ""), "x")
colnames(mor_me) <- c("cause0", "cause", "sgg_cd", "sgg_nm", "sex0", "sex", "type0", "type", "unit", paste("Y", 1998:2019, sep = ""), "x")
colnames(mor_fe) <- c("cause0", "cause", "sgg_cd", "sgg_nm", "sex0", "sex", "type0", "type", "unit", paste("Y", 1998:2019, sep = ""), "x")


## Data preprocessing ####
sgg <- st_read(paste(geopath, "SGG_Merge_2000_2016.shp", sep = ""))
sgg2010 <- sgg %>%
    filter(BASE_YEAR == 2010)
conv_table_e = conv_table %>%
    filter(from_year >= 1999 & from_year <= 2013) %>%
    dplyr::select(fromcode, tocode)

pop_cl = pop %>%
    mutate(sgg_cd = plyr::mapvalues(sgg_cd, conv_table_e$fromcode, conv_table_e$tocode),
           year_agg = cut(year, breaks = c(1998,2003,2008,2013,2018,2019), labels = c('1999-2003', '2004-2008', '2009-2013', '2014-2018', '2019'), right = TRUE)) %>%
    group_by(year_agg, sgg_cd, sex0, sex_e) %>%
    summarize(population = sum(population, na.rm = TRUE)) %>%
    ungroup


inc_cl <- inc %>%
    mutate(
        n_n = as.numeric(n),
        n_n = ifelse(is.na(n_n), 0, n_n),
        cancer_type_e = plyr::mapvalues(cancer_type, unique(cancer_type), c("Stomach", "Colorectal", "Liver", "Lung", "Breast", "Cervical", "Prostate", "Thyroid")),
        sex_e = plyr::mapvalues(sex, unique(sex), c("Total", "Male", "Female")),
        type_inc_e = plyr::mapvalues(type_inc, unique(type_inc), c("N", "r_crude", "r_agest")),
        sgg_cd_c = plyr::mapvalues(sgg_cd, conv_table_e$fromcode, conv_table_e$tocode)
    ) %>%
    # not sum
    pivot_wider(id_cols = c(year, sgg_cd_c, cancer_type_e, sex_e), names_from = type_inc_e, values_from = n_n, values_fn = function(x) sum(x, na.rm = TRUE)) %>%
    # note that sex-specific cancers have incorrect crude rates
    left_join(pop_cl, by = c('year' = 'year_agg', 'sgg_cd_c' = 'sgg_cd', 'sex_e' = 'sex_e')) %>%
    group_by(year, sgg_cd_c, cancer_type_e, sex_e) %>%
    summarize(Ntotal = sum(N, na.rm = T),
              r_crude = sum(r_crude * (population / sum(population, na.rm = T)), na.rm = T)) %>%
    ungroup %>%
    pivot_longer(cols = 5:6, values_to = 'n_n', names_to = 'type_inc_e')

# summary table
inc_cl_summary <- inc_cl %>%
    group_by(cancer_type_e, year, sex_e, type_inc_e) %>%
    summarize(
        n_nmin = min(n_n),
        n_nmedian = median(n_n),
        n_nmean = mean(n_n),
        n_nmax = max(n_n)
    ) %>%
    ungroup() %>%
    pivot_longer(cols = 5:8) %>%
    pivot_wider(names_from = c("sex_e", "name"))

mor_cl = bind_rows(mor_to, mor_me) %>%
    bind_rows(mor_fe) %>%
    pivot_longer(cols = Y1998:Y2019) %>%
    mutate(year = as.integer(str_sub(name, 2, 5)),
           year_agg = cut(year, breaks = c(1998,2003,2008,2013,2018,2019), labels = c('1999-2003', '2004-2008', '2009-2013', '2014-2018', '2019'), right = TRUE),
           cancer_type_e = plyr::mapvalues(cause, unique(cause), c("Stomach", "Colorectal", "Liver", "Lung/Bronchus", "Breast", "Cervical/Uterine", "Prostate")),
           sex_e = plyr::mapvalues(sex, unique(sex), c('Total', 'Male', 'Female')),
           type_mor_e = plyr::mapvalues(type0, c('T1', 'T4', 'T7'), c('N', 'r_crude', 'r_agest')),
           sgg_cd_c = plyr::mapvalues(sgg_cd, conv_table_e$fromcode, conv_table_e$tocode)
        ) %>%
    # not sum
    pivot_wider(id_cols = c(year_agg, sgg_cd_c, cancer_type_e, sex_e), names_from = type_mor_e, values_from = value, values_fn = function(x) sum(x, na.rm = TRUE)) %>%
    left_join(pop_cl, by = c('year_agg' = 'year_agg', 'sgg_cd_c' = 'sgg_cd', 'sex_e' = 'sex_e')) %>%
    group_by(year_agg, sgg_cd_c, cancer_type_e, sex_e) %>%
    summarize(Ntotal = sum(N, na.rm = T),
              r_crude = 1e5 * sum(N, na.rm = T)/sum(population, na.rm = T)) %>%
    ungroup %>%
    filter(year_agg %in% c('1999-2003', '2004-2008', '2009-2013'))
```

```{r Aggregated data: pop mort inc, include = FALSE, eval = FALSE}
### Incidence-Mortality consolidation ####
## Mortality
mor_clw = mor_cl %>%
    filter(cancer_type_e %in% c('Stomach', 'Lung/Bronchus')) %>%
    mutate(sex_e = tolower(sex_e),
           cancer_type_e = ifelse(cancer_type_e == 'Lung/Bronchus', 'Lung', cancer_type_e)) %>%
    rename(n = Ntotal) %>%
    mutate(period = plyr::mapvalues(year_agg, unique(year_agg), seq_len(length(unique(year_agg))))) %>%
    dplyr::select(-year_agg, -r_crude) %>%
    filter(period %in% 1:3) %>%
    pivot_wider(names_from = c(cancer_type_e, sex_e, period),
                names_sep = "_",
                names_prefix = "n_d_",
                values_from = n)    

## Incidence
inc_clw = inc_cl %>%
    filter(cancer_type_e %in% c('Stomach', 'Lung') & type_inc_e == "Ntotal") %>%
    mutate(sex_e = tolower(sex_e),
           type_inc_e = 'n') %>%
    mutate(period = plyr::mapvalues(year, unique(year), seq_len(length(unique(year))))) %>%
    dplyr::select(-year, -type_inc_e) %>%
    pivot_wider(names_from = c(cancer_type_e, sex_e, period),
                names_sep = "_",
                names_prefix = 'n_i_',
                values_from = n_n)    

## Population (5-year aggregation)
pop_clw = pop_cl %>%
    mutate(sex_e = tolower(sex_e),
           period = plyr::mapvalues(year_agg, unique(year_agg), seq_len(length(unique(year_agg))))) %>%
    dplyr::select(-sex0, -year_agg) %>%
    filter(period %in% 1:3) %>%
    pivot_wider(names_from = c(sex_e, period),
                names_sep = "_",
                names_prefix = 'n_p_',
                values_from = population) %>%
    dplyr::select(-ends_with('_NA'))


## Joined mortality-incidence-population (5-year aggregated)
morinc_clw = mor_clw %>%
    full_join(inc_clw) %>%
    full_join(pop_clw, by = c('sgg_cd_c' = 'sgg_cd'))

```


```{r Summary plots}
inc_clgg_n = inc_cl %>%
    filter(cancer_type_e %in% c('Lung', 'Stomach') & type_inc_e == 'Ntotal') %>%
    ggplot(data = .,
           mapping = aes(x = year, y = n_n, group = interaction(year, cancer_type_e, sex_e))) +
        facet_grid(sex_e ~ cancer_type_e) +
        geom_boxplot() +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        #scale_y_continuous(limits = c(0, 225)) +
        labs(subtitle = 'Crude cancer incidence counts by five-year periods and types')

inc_clgg_r = inc_cl %>%
    filter(cancer_type_e %in% c('Lung', 'Stomach') & type_inc_e == 'r_crude') %>%
    ggplot(data = .,
           mapping = aes(x = year, y = n_n, group = interaction(year, cancer_type_e, sex_e))) +
        facet_grid(sex_e ~ cancer_type_e) +
        geom_boxplot() +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        #scale_y_continuous(limits = c(0, 225)) +
        labs(subtitle = 'Crude cancer incidence rates per 100,000 persons by five-year periods and types')


mor_clgg_n = mor_cl %>%
    filter(cancer_type_e %in% c('Lung/Bronchus', 'Stomach')) %>%
    #left_join(pop, by = c('sgg_cd' = 'sgg_cd', 'year' = 'year', 'sex_e' = 'sex_e')) %>%
    #group_by(sgg_cd, cause, cancer_type_e, sex_e, year_agg) %>%
    #summarize(rate_100k_5yr = 1e5 * (sum(value, na.rm = T)/sum(population, na.rm = T))) %>%
    #ungroup %>%
    ggplot(data = .,
           mapping = aes(x= year_agg, y = Ntotal, group = interaction(year_agg, cancer_type_e, sex_e))) +
        facet_grid(sex_e ~ cancer_type_e) +
        geom_boxplot() +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        #scale_y_continuous(limits = c(0, 225)) +
        labs(subtitle = 'Cancer mortality counts by years and types')


mor_clgg_r = mor_cl %>%
    filter(cancer_type_e %in% c('Lung/Bronchus', 'Stomach')) %>%
    #left_join(pop, by = c('sgg_cd' = 'sgg_cd', 'year' = 'year', 'sex_e' = 'sex_e')) %>%
    #group_by(sgg_cd, cause, cancer_type_e, sex_e, year_agg) %>%
    #summarize(rate_100k_5yr = 1e5 * (sum(value, na.rm = T)/sum(population, na.rm = T))) %>%
    #ungroup %>%
    ggplot(data = .,
           mapping = aes(x= year_agg, y = r_crude, group = interaction(year_agg, cancer_type_e, sex_e))) +
        facet_grid(sex_e ~ cancer_type_e) +
        geom_boxplot() +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        #scale_y_continuous(limits = c(0, 225)) +
        labs(subtitle = 'Crude cancer mortality rates per 100,000 persons by years and types')

(inc_clgg_n | mor_clgg_n)

(inc_clgg_r | mor_clgg_r)

```


```{r}
#load('Scan_SMERC_2009_2013_Results.RData')
#load('Scan_DCLUST_2009_2013_Results.RData')
load(str_c(drive, '/Manuscript/Clustering_Base_sf_021722.RData'))
#load(str_c(drive, '/Manuscript/Scan_SMERC_periods_1_3_vsets_1_2_Results_p005.RData'))
#load(str_c(drive, '/Manuscript/Scan_SMERC_periods_2_3_vsets_3_4_Results_p005.RData'))
load(str_c(drive, '/Manuscript/Scan_SMERC_periods_1_3_vsets_1_4_Results_35p_p001.RData'))

covar_origin_10_fc = covar_origin_10_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430)) %>%
    ms_simplify(keep = 0.125, keep_shapes = TRUE)
covar_origin_05_fc = covar_origin_05_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430)) %>%
    ms_simplify(keep = 0.125, keep_shapes = TRUE)
covar_origin_00_fc = covar_origin_00_fc %>%
    filter(!sgg_cd_c %in% c(23320, 37430)) %>%
    ms_simplify(keep = 0.125, keep_shapes = TRUE)



```

# Overview
- Incidence and mortality rates: (Sum of cases) / (Sum of the population)
- All inclusive variables
    - Set 1: elderly population rate (%) and higher than bachelor's degree (%)
    - Set 2: Set 1 + including emission, residential exposure, and NDVI
    - Set 3: for periods 2 and 3. All but insurance premium and stomach cancer screening
    - Set 4: for period 3 only. All variables.

# Lung Cancer
## All sexes
```{r Lung cancer cluster plots, fig.width=10, fig.height = 10}
tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_lung_1itu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, All sexes, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1it_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, All sexes, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1it_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, All sexes, Variable set 2)  ', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2itu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, All sexes, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2it_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, All sexes, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2it_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, All sexes, Variable set 2)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2it_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, All sexes, Variable set 3)  ', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3itu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, All sexes, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3it_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, All sexes, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3it_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, All sexes, Variable set 2)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3it_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, All sexes, Variable set 3)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3it_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, All sexes, Variable set 4)  ', frame = FALSE),
    ncol = 5
)

## One-shot
tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_lung_1dtu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1dt_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1dt_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, All sexes, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dtu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dt_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dt_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, All sexes, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dt_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, All sexes, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dtu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dt_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dt_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, All sexes, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dt_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, All sexes, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dt_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, All sexes, Variable set 4)', frame = FALSE),
    ncol = 5
)


```

## Female
```{r Lung: sex stratified (female), fig.width=10, fig.height = 10}

tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_lung_1ifu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Female, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1if_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Female, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1if_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Female, Variable set 2)  ', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2ifu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Female, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2if_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Female, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2if_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Female, Variable set 2)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2if_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Female, Variable set 3)  ', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3ifu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Female, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3if_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Female, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3if_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Female, Variable set 2)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3if_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Female, Variable set 3)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3if_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Female, Variable set 4)  ', frame = FALSE),
    ncol = 5
)

## One-shot
tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_lung_1dfu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1df_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1df_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Female, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dfu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2df_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2df_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Female, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2df_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Female, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dfu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3df_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3df_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Female, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3df_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Female, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3df_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Female, Variable set 4)', frame = FALSE),
    ncol = 5
)

```

## Male
```{r Lung: sex stratified (male), fig.width=10, fig.height = 10}

tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_lung_1imu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Male, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1im_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Male, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1im_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(1999-2003, Male, Variable set 2)  ', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2imu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Male, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2im_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Male, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2im_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Male, Variable set 2)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2im_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2004-2008, Male, Variable set 3)  ', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3imu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Male, Uncontrolled)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3im_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Male, Variable set 1)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3im_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Male, Variable set 2)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3im_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Male, Variable set 3)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3im_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer incidence\n(2009-2013, Male, Variable set 4)  ', frame = FALSE),
    ncol = 5
)

## One-shot
tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_lung_1dmu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1dm_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_lung_1dm_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(1999-2003, Male, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dmu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dm_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dm_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Male, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_lung_2dm_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2004-2008, Male, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dmu, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dm_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dm_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Male, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dm_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Male, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_lung_3dm_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Lung cancer mortality\n(2009-2013, Male, Variable set 4)', frame = FALSE),
    ncol = 5
)

```


# Stomach cancer
## All sexes
```{r Stomach cancer cluster plots, fig.width=12, fig.height = 9}
tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_stom_1itu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1it_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1it_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, All sexes, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2itu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2it_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2it_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, All sexes, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2it_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, All sexes, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3itu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3it_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3it_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, All sexes, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3it_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, All sexes, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3it_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, All sexes, Variable set 4)', frame = FALSE),
    ncol = 5
)


tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_stom_1dtu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1dt_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1dt_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, All sexes, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dtu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dt_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dt_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, All sexes, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dt_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, All sexes, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dtu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, All sexes, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dt_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, All sexes, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dt_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, All sexes, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dt_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, All sexes, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dt_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, All sexes, Variable set 4)', frame = FALSE),
    ncol = 5
)

```

## Female
```{r Stomach (female), fig.width=10, fig.height = 10}
tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_stom_1ifu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1if_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1if_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Female, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2ifu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2if_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2if_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Female, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2if_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Female, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3ifu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3if_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3if_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Female, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3if_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Female, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3if_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Female, Variable set 4)', frame = FALSE),
    ncol = 5
)


tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_stom_1dfu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1df_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1df_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Female, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dfu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2df_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2df_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Female, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2df_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Female, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dfu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Female, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3df_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Female, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3df_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Female, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3df_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Female, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3df_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Female, Variable set 4)', frame = FALSE),
    ncol = 5
)


```


## Male
```{r Stomach (Male), fig.width=10, fig.height = 10}
tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_stom_1imu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1im_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1im_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(1999-2003, Male, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2imu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2im_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2im_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Male, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2im_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2004-2008, Male, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3imu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3im_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3im_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Male, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3im_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Male, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3im_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer incidence\n(2009-2013, Male, Variable set 4)', frame = FALSE),
    ncol = 5
)


tmap::tmap_arrange(
    tmap_smerc(covar_origin_00_fc, smerc_stom_1dmu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1dm_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_00_fc, smerc_stom_1dm_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(1999-2003, Male, Variable set 2)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dmu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dm_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dm_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Male, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_05_fc, smerc_stom_2dm_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2004-2008, Male, Variable set 3)', frame = FALSE),
    tm_shape(covar_origin_00_fc) + tm_borders('transparent') + tm_layout(frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dmu, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Male, Uncontrolled)  ', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dm_v1, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Male, Variable set 1)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dm_v2, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Male, Variable set 2)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dm_v3, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Male, Variable set 3)', frame = FALSE),
    tmap_smerc(covar_origin_10_fc, smerc_stom_3dm_v4, return_ellipses = TRUE) + 
        tm_layout(title = 'Stomach cancer mortality\n(2009-2013, Male, Variable set 4)', frame = FALSE),
    ncol = 5
)



```



# Tables for regression analysis (Lung cancer)
```{r Tables for regression analysis, results = "asis", eval = FALSE, include = FALSE}
reg_lung_3it = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_total_3', population = 'n_p_total_3', sex_b = 'total')
reg_stom_3it = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_total_3', population = 'n_p_total_3', sex_b = 'total', add_var = 'p_candiag_sto')
reg_lung_3im = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_male_3', population = 'n_p_male_3', sex_b = 'male')
reg_stom_3im = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_male_3', population = 'n_p_male_3', sex_b = 'male', add_var = 'p_candiag_sto')
reg_lung_3if = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_female_3', population = 'n_p_female_3', sex_b = 'female')
reg_stom_3if = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_female_3', population = 'n_p_female_3', sex_b = 'female', add_var = 'p_candiag_sto')

reg_lung_3it = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_total_3', population = 'n_p_total_3', sex_b = 'total')
reg_stom_3it = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_total_3', population = 'n_p_total_3', sex_b = 'total', add_var = 'p_candiag_sto')
reg_lung_3im = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_male_3', population = 'n_p_male_3', sex_b = 'male')
reg_stom_3im = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_male_3', population = 'n_p_male_3', sex_b = 'male', add_var = 'p_candiag_sto')
reg_lung_3if = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_female_3', population = 'n_p_female_3', sex_b = 'female')
reg_stom_3if = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_female_3', population = 'n_p_female_3', sex_b = 'female', add_var = 'p_candiag_sto')

reg_lung_3it = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_total_3', population = 'n_p_total_3', sex_b = 'total')
reg_stom_3it = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_total_3', population = 'n_p_total_3', sex_b = 'total', add_var = 'p_candiag_sto')
reg_lung_3im = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_male_3', population = 'n_p_male_3', sex_b = 'male')
reg_stom_3im = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_male_3', population = 'n_p_male_3', sex_b = 'male', add_var = 'p_candiag_sto')
reg_lung_3if = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Lung_female_3', population = 'n_p_female_3', sex_b = 'female')
reg_stom_3if = regress_counts(data = covar_origin_10_fc, yvar = 'n_i_Stomach_female_3', population = 'n_p_female_3', sex_b = 'female', add_var = 'p_candiag_sto')


# Mortality (d)
reg_lung_3dt = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_total_3', population = 'n_p_total_3', sex_b = 'total')
reg_stom_3dt = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_total_3', population = 'n_p_total_3', sex_b = 'total', add_var = 'p_candiag_sto')
reg_lung_3dm = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_male_3', population = 'n_p_male_3', sex_b = 'male')
reg_stom_3dm = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_male_3', population = 'n_p_male_3', sex_b = 'male', add_var = 'p_candiag_sto')
reg_lung_3df = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_female_3', population = 'n_p_female_3', sex_b = 'female')
reg_stom_3df = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_female_3', population = 'n_p_female_3', sex_b = 'female', add_var = 'p_candiag_sto')

reg_lung_3dt = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_total_3', population = 'n_p_total_3', sex_b = 'total')
reg_stom_3dt = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_total_3', population = 'n_p_total_3', sex_b = 'total', add_var = 'p_candiag_sto')
reg_lung_3dm = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_male_3', population = 'n_p_male_3', sex_b = 'male')
reg_stom_3dm = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_male_3', population = 'n_p_male_3', sex_b = 'male', add_var = 'p_candiag_sto')
reg_lung_3df = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_female_3', population = 'n_p_female_3', sex_b = 'female')
reg_stom_3df = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_female_3', population = 'n_p_female_3', sex_b = 'female', add_var = 'p_candiag_sto')

reg_lung_3dt = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_total_3', population = 'n_p_total_3', sex_b = 'total')
reg_stom_3dt = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_total_3', population = 'n_p_total_3', sex_b = 'total', add_var = 'p_candiag_sto')
reg_lung_3dm = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_male_3', population = 'n_p_male_3', sex_b = 'male')
reg_stom_3dm = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_male_3', population = 'n_p_male_3', sex_b = 'male', add_var = 'p_candiag_sto')
reg_lung_3df = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Lung_female_3', population = 'n_p_female_3', sex_b = 'female')
reg_stom_3df = regress_counts(data = covar_origin_10_fc, yvar = 'n_d_Stomach_female_3', population = 'n_p_female_3', sex_b = 'female', add_var = 'p_candiag_sto')


description = data.frame(
    Variable = names(reg_stom_3dt$coefficients)[-1],
    Description = c("Higher than bachelor's degree (%)",
                    "Stomach cancer diagnosis rate (%; only included in stomach cancer models)",
                    "Older than 65 years old (%)",
                    "Unemployment rate (%)",
                    "Change rate of land price (%)",
                    "Walking regularly (%)",
                    "Obesity rate (%)",
                    "Alcohol consumption rate (%; more frequent than once a month)",
                    "Physical activity rate (%)",
                    "Smoking (%)",
                    "Average PM10 exposure",
                    "Average NO2 exposure",
                    "Average NDVI (unitless)",
                    "Total CO emission",
                    "Total NOx emission",
                    "Total SOx emission",
                    "Total TSP emission",
                    "Total PM10 emission",
                    "Total VOC emission",
                    "Total NH3 emission"),
    Set = c(1, 4, 1, 3, 3, 3, 3, 3, 3, 3, 2, 2, 2, 2, 2, 2, 2, 2, 2, 2)
)

kable(description %>% arrange(Set), format = "html")

macro_stargazer = function(reg_results,
                           title1 = "cancer") {
    
    stargazer(reg_results[[1]], reg_results[[2]],
              type = "html",
              title = sprintf("Poisson regression models of %s for incidence and mortality", title1),
              column.labels = c("Incidence", "Mortality"),
              colnames = FALSE,
              header = FALSE,
              model.numbers = FALSE,
              keep.stat = c("aic", "f"),
              notes.align = 'l')
    }
```



```{r Tables: lung cancer, results = 'asis', eval = FALSE}
macro_stargazer(list(reg_lung_1it, reg_lung_1dt), "lung cancer (P1, all sexes)")
macro_stargazer(list(reg_lung_1if, reg_lung_1df), "lung cancer (P1, female)")
macro_stargazer(list(reg_lung_1im, reg_lung_1dm), "lung cancer (P1, male)")


macro_stargazer(list(reg_lung_2it, reg_lung_2dt), "lung cancer (P2, all sexes)")
macro_stargazer(list(reg_lung_2if, reg_lung_2df), "lung cancer (P2, female)")
macro_stargazer(list(reg_lung_2im, reg_lung_2dm), "lung cancer (P2, male)")


macro_stargazer(list(reg_lung_3it, reg_lung_3dt), "lung cancer (P3, all sexes)")
macro_stargazer(list(reg_lung_3if, reg_lung_3df), "lung cancer (P3, female)")
macro_stargazer(list(reg_lung_3im, reg_lung_3dm), "lung cancer (P3, male)")

```


# Tables for regression analysis (Stomach cancer)
```{r Tables: stomach cancer, results = 'asis', eval = FALSE}
macro_stargazer(list(reg_stom_1it, reg_stom_1dt), "stomach cancer (P1, all sexes)")
macro_stargazer(list(reg_stom_1if, reg_stom_1df), "stomach cancer (P1, female)")
macro_stargazer(list(reg_stom_1im, reg_stom_1dm), "stomach cancer (P1, male)")

macro_stargazer(list(reg_stom_2it, reg_stom_2dt), "stomach cancer (P2, all sexes)")
macro_stargazer(list(reg_stom_2if, reg_stom_2df), "stomach cancer (P2, female)")
macro_stargazer(list(reg_stom_2im, reg_stom_2dm), "stomach cancer (P2, male)")

macro_stargazer(list(reg_stom_3it, reg_stom_3dt), "stomach cancer (P3, all sexes)")
macro_stargazer(list(reg_stom_3if, reg_stom_3df), "stomach cancer (P3, female)")
macro_stargazer(list(reg_stom_3im, reg_stom_3dm), "stomach cancer (P3, male)")


```